---
title: "Stat506_PS1 Part 2 & 3   Meng-Ni Ho" 
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(sqldf)
library(nycflights13)
library(ggplot2)
setwd("~/Desktop/STAT506/ps1")
source("ps1_q2.R")
source("ps1_q3.R")
```

## Question 2a
Which airlines were responsible for at least 1% of the flights 
departing any of the three NYC airports between January 1 and October 31, 2013?

```{r, echo = FALSE}
q2_1_2
```


## Question 2b
Among the airlines from part “a”, compare the number and percent of annual flights in the first 10 months of 2013 and the first 10 months of 2014. 

```{r, echo = FALSE}
merge1
```

1. Which airline showed the largest increase?
```{r}
sqldf("select carrier, name, max(p_change) from merge1")
```

2. Which airline showed the largest decrease?
```{r}
sqldf("select carrier, name, min(p_change) from merge1")
```

3. Why do some airlines show an increase in the percent of flights but a decrease in the number of flights?

Becasue total flights in 2014 decreased compared to 2013, then for the airlines that showed decreased flights, their percentage will increase.




##Question 2c
Among of the three NYC airports, produce a table showing the percent of flights each airline is responsible for. 
Limit the table to the airlines identified in part a and include confidence intervals for your estimates. 

```{r, echo = FALSE}
merge2
```

* Which airline is the largest carrier at each airport?
```{r}
sqldf("select origin, carrier, max(proportion) as max_ from merge2 group by origin")
```


##Question 3a
What percent of homes have stucco construction as the major outside wall material within each division? 

```{r, echo = FALSE}
stucco_wall_prop
```


1. Which division has the highest proportion?
```{r}
sqldf("select DIVISION, max(pct) as max_percentage from stucco_wall_prop")
```

2. Which division has the lowest proportion?
```{r}
sqldf("select DIVISION, min(pct) as min_percentage from stucco_wall_prop")
```



```{r plot, echo = FALSE}
g_q3_1
```

* Plot: % of having STUCCO as major walltype in each division



## Question 3b
1. What is average total electricity usage in kilowatt hours in each division? 
```{r, echo = FALSE}
q3_2_1
```



```{r, echo = FALSE}
g_q3_2
```

* Plot: Average electricity usage in each division


2. What is average total electricity usage in kilowatt hours in each division stratified by urban and rural? 

```{r, echo = FALSE}
q3_2_2
```




```{r, echo = FALSE}
g_q3_2_2
```
* Plot: average total electricity usage in kilowatt hours in each division stratified by urban and rural


## Question 3c
Which division has the largest disparity between urban and rural areas in terms of proportion of homes with internet access?

* Table showing disparity (urban vs rural) in terms of the proportion of homes with internet access?
```{r, echo = FALSE}
disparity
```


* Which division has the largest disparity between urban and rural areas in terms of the proportion of homes with internet access?
```{r, echo = FALSE}
sqldf("select DIVISION, max(disparity) from disparity")
```

```{r, echo = FALSE}
g_q3_3
```
* Plot: proportion of homes with internet access between urban and rural in each division

