---
title: "STAT 506 problem set 2 Meng-Ni Ho"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(stargazer)
source("ps2_q3.R")
```

# Question 1: estimates, replicate standard error, 95% confidence interval for recs2015 data
1. Electricity usage in kilowatt hours: kwh
2. Natural gas usage, in hundreds of cubic feet: cufeetng
3. Propane usage, in gallons: gallonlp
4. Fuel oil or kerosene usage, in gallons: gallonfo



```{r table, echo=FALSE}
recs = read.csv("recs2015_usage.csv")
recs$lower_bound = recs$estimate - qnorm(.975)*recs$replicate_standard_error
recs$upper_bound = recs$estimate + qnorm(.975)*recs$replicate_standard_error
recs$estimate = round(recs$estimate, digits = 2)
recs$variance = round(recs$variance, digits = 2)
recs$replicate_standard_error = round(recs$replicate_standard_error, digits = 2)
recs$lower_bound = round(recs$lower_bound, digits = 2)
recs$upper_bound = round(recs$upper_bound, digits = 2)

recs = kable(recs)
recs
```

#Question 2: fitting model using stata
representative age in part b is calculated using R

#Question 3: fitting model using R
##Part b:
* model1: null model, BIC = 1533.407
  1. dependent variable: probability of individual lose their primary upper right 2nd bicuspid (outcome)
  2. independent variable: age in months (ridagem)

```{r, echo = FALSE}
model1
```

* Use fitted model to estimate ages (in months) in p = 0.25, 0.50, 0.75
  1. when p = 0.25
```{r, echo = FALSE}
age25
```
  2. when p = 0.50
```{r, echo = FALSE}
age50
```
  3. when p = 0.75
```{r, echo = FALSE}
age75
```

* representative age (25%, 75%) in years:
```{r, echo = FALSE}
age
```


##Part C
* model2: BIC = 1542.055 
add gender (riagendr) to model 1, since BIC increase, gender is excluded from the model


* model3: BIC = 1542.285
add race_1 (race = Mexican is coded 1, all other race coded 0) to the model1, since BIC increase, race_1 is excluded from the model

* model4: BIC = 1541.932
add race_2 (other hispanic and other race is coded 1, all other race coded 0) to model1, since BIC increase from model1, race_2 is excluded from the model

* model5: BIC = 1529.281
add race_3 (non-hispanic black is coded 1, all other race coded 0) to model4, since BIC decrease from model1, race_3 is retained in the model

* model6 (final model): BIC = 1462.895 
add poverty income ratio (indfmpir) to model5, since BIC decrease from model5, poverty income ratio is retained in the model

final model:   
```{r, echo = FALSE}
model6
```

##Part D
1. Adjusted predictions at the mean (for other values) at each of the representative ages determined in part b.

* adjsuted predictions at representative age = 8
```{r, echo = F}
pr_age25
```

* adjsuted predictions at representative age = 12
```{r, echo = F}
pr_age75
```


2. The marginal effects at the mean of any retained categorical variables at the same representative ages.
* marginal effect at representative age = 8
```{r, echo = F}
mse_25
```

* marginal effect at representative age = 12
```{r, echo = F}
mse_75
```


3. The average marginal effect of any retained categorical variables at the representative ages.

```{r, echo = F}
ame
```




